\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Quentin DIDIER} \\ \vspace{1pt}
    Technical Project Manager \& Transformation Lead  \\
    — \emph{I help teams debug complex technical and organizational problems} — \\
    Paris, France — open to Remote \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +33 6 61 20 19 15 ~ 
    \href{mailto:quentin.didier708@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{quentin.didier708@gmail.com} }
    \href{https://www.linkedin.com/in/quentin-didier-521376197/}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}}
    \vspace{-8pt}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {Freelance}{September 2023 - Now}
      {}{} 
      \resumeItemListStart
      \vspace{-14pt}
        % --- Project Consulting ---
    \resumeItem{\textbf{Project Consulting} — Improved decision-making and execution systems in growing organizations and technical teams by diagnosing coordination failures, unclear ownership and goals.}
    \resumeItem{Audited a policy-oriented research agenda, clarifying research priorities, theory of change, and evaluation criteria.}
    \resumeItem{Guided an indie game developer on game design and audience engagement: iterating on game loops, level design, and content distribution strategy.}

    % --- Internal Tools & Operations Software ---
    \resumeItem{\textbf{Internal Tools \&  Software development} —Designed and deployed internal execution systems, replacing manual workflows with structured tools (Notion, Airtable, Power Apps, Google Apps, custom web apps)}
    \resumeItem{Automated workflows over structured datasets (contacts, partners, grants, projects), reducing manual handling and inconsistencies.}
    \resumeItem{Built an internal budgeting, invoicing, and purchase-order management system for a small organization.}
    \resumeItem{Delivered small-to-mid scale web development projects (Next.js, TypeScript), including websites and automated accounting and reporting tools for private tutors.}

     
      \resumeItemListEnd
      \vspace{-4pt}

    \resumeSubheading
      {Projects Director \& AI Safety Unit Director}{July 2022 -- September 2023}
      {Collectif Effisciences}{Paris, France}
      \resumeItemListStart
        \resumeItem{\textbf{Launched \& organized a wide portfolio of 30+ projects} (Research programs, courses, conferences, etc) in artificial intelligence security and biosecurity, in France and Europe, managing a team of around twenty collaborators.}
        \resumeItem{\textbf{Shaped organizational strategy} at org scale and for each units (Climate Change, Biosecurity, transversal projects), restructured the organization's communication and task management systems.}
        \resumeItem{\textbf{Organized 3 large hackathons with 150+ participants} (Ecole 42, Collège de France, Entrepreneur First) and a number of smaller hackathons with various partners, research groups, conferences, developing collaborations with public and private actors (UNESCO, Institut Pasteur, Meta, ENS, etc).}
        \resumeItem{\textbf{Designed \& delivered Master's level classes at ENS Ulm} and Saclay (MVA Master's program), designed and taught technical AI safety curricula to top performing students, delivered talks and workshops.}
      \resumeItemListEnd

    \resumeSubheading
      {Research Intern - Theoretical frameworks for robotics}{Summer 2019}
      {ISIR - Sorbonne Université}{Paris, France}
      \resumeItemListStart
        \resumeItem{Theoretical analysis of various learning methods for robotics (Novelty Search, Goal Exploration Processes, MAP-Elites).}
%        \resumeItem{Implementation in Python}
      \resumeItemListEnd
\begin{comment}
    \resumeSubheading
      {Research Intern - Statistical learning}{Summer 2018}
      {LPSM - Université Paris Diderot}{Paris, France}
      \resumeItemListStart
        \resumeItem{Explored unsupervised Random Forest methods on single-cell gene expression data for tumor classification.
}
        \resumeItem{Implementation in Python and R.}
      \resumeItemListEnd
\end{comment}
    \resumeSubheading
      {Board Member - Secretary General}{2022 - 2023}
      {Altruisme Efficace France}{Paris, France}
      \resumeItemListStart
        \resumeItem{Defined annual priorities and strategic initiatives for the organization’s missions in global health, pandemic preparedness, animal welfare and artificial intelligence safety.}
        \resumeItem{Led organization's operations, managing a remote team of 2 employees and 40+ active volunteers, handled staff recruitment. Organized biannual retreats, weekly events, ran an academic fellowship}
      \resumeItemListEnd

      \resumeSubheading
      {Private teacher}{2021 - Now}
      {Mathematics, Computer Science, Physics, Biology}{}
      \resumeItemListStart
        \resumeItem{Private tutoring for about 30 students over 4 years ranging from primary school to Master's level.}
      \resumeItemListEnd
      
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Double Master's degree, first year: Data Science and Cryptography}{2021 -- 2023}
      {Paused degree after the first year to build Effisciences full time.}{Université de Paris}
      \vspace{-3pt}
    \resumeSubheading
      {Bachelor's degree in Computer Science - Université de Besançon}{2020 -- 2021}
      {}{}
      \vspace{-16pt}
    \resumeSubheading
      {Master's degree in Applied Mathematics, first year - Université Paris V}{2019 -- 2020}
      {}{}
      \vspace{-16pt}
    \resumeSubheading
      {Bachelor's Degree in Mathematics - Université de Strasbourg}{2015 -- 2018}
      {}{}
      \vspace{-20pt}
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Programming}{: Python, C/C++, HTML/CSS/SCSS, JavaScript, R, Rust (Basic)} \\
     \textbf{Languages}{: French (Native), English (Fluent), Spanish (B1), Mandarin (A2), German (A2)}
    }}
 \end{itemize}
 \vspace{-16pt}
 

%-----------INTERESTS-----------
\section{Interests}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Scientific}{: History of Science, Physics, Biology, Economics, Finance, History, Cognitive Sciences, Epistemology} \\
     \textbf{Arts \& Activities}{: Literature (Russian, SF, Poetry), Game of Go, Guitar, Weightlifting, Knitting, Juggling, Meditation, Dancing, Watercolor, Violin, Analog Photography}
    }}
 \end{itemize}

\end{document}      